---
title: 'Q1'
author: "WeW"
date: "1 October 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# R lang
##  What does this statement produce

```{r}
a <- c(2,3,4) 
b <- c(1,2)

```


## What does this code do?

```{r}
a <- c(1,1,1,1,2,2,2,2,2)
b <- c(10,12,15,12,NA,30,42,38,40)
s <- split(b,a)
lapply(s, mean)
```



## dplyr

```{r}
library(dplyr)

x <-data.frame(a = 1:10, b=3:12)

x %>% group_by(a,b) %>% select(a)
x %>% select(a)
```

Is the results of the two expressions the same. If not what can you do to make it the same?

## Data Structures - lists

How would you create an empty list of length 100?
```{r}

as.list(rep(NA,100))
vector(100, mode="list")

```

## Data Structures - matrices

What is the result of?

```{r}
x <- matrix(1:4, nrow=2)
x
y <- matrix(1:4, ncol=2)
y
```

and of:

```{r}
x[2,2] <- NA
na.omit(x)
```

## What is the result of?

```{r}
dim(1:3)

```

## distribution functions

what are the r-functions for?

- `dnorm`
- `pnorm`
- `qnorm`
- `rnorm`

What is common and what are the differences?

# Programming general

## naming functions

How do you name functions and why?

## What is git and why do you want to use it in your work?

## How do you work with git? 

Show the process of making a commit and pushing to a repository.
(describe it, exact syntax not required)

What does _revert_ mean?

## Contributing on github 

How (on github) you can contribute to a repository without write permissions?
(describe it in your own words)

## R packages

In your CV you wrote R-packages - do you mean use or development? 
What do you like or dislike about them - pros and cons

## Basic principles

How would you improve that code?

```
> rmarkdown::render("BenchmarkingMQ.Rmd")


processing file: BenchmarkingMQ.Rmd
  |...                                                              |   5%
  ordinary text without R code

  |......                                                           |   9%
label: unnamed-chunk-1 (with options) 
List of 1
 $ include: logi FALSE

Quitting from lines 8-240 (BenchmarkingMQ.Rmd) 
Error in dataset[, -12:-21] : incorrect number of dimensions
```

## Design

Assume you have an R-markdown which does some matrix visualization. 
It also includes a  heatmap with row and column dendrograms.
You are asked to cut the row dendrogram, shown in the figure into N clusters (a user parameter) and to store the results 
into a file containing the `row lables` and the cluster id 1:N.

How would you implement it?

This questions is not about the code needed to cut the dendrogram.
(not about `cutree(hclust(dist(X)))`.)

It is about the program flow, how you store the information you need for the task and where you store the results, and when you would write them.

There is no single correct answer.








